Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-07-16 paper/main.tex
additional edits to section 2.2.1

Importantly, packages installed by Davos are made available for use in the
notebook without affecting the user's Python environment. By default,
\texttt{smuggle} statements install missing packages (and any missing
dependencies of those packages) into a notebook-specific, virtual
environment-like directory called a ``project'' (see
Sec.~\ref{subsec:projects}). When a \texttt{smuggle} statement in a particular
notebook is executed, Davos will first check for the smuggled package in that
notebook's corresponding project directory before searching the user's main
Python environment. In this way, \texttt{smuggle} statements can be substituted
for \texttt{import} statements to automatically ensure that all packages needed
to run a notebook are installed and available at runtime without risking
interfering with dependencies of the user's other Python programs, or other
Davos-enhanced notebooks.

>>>>

Importantly, packages installed by Davos are made available for use in the
notebook without affecting the user's Python environment or existing packages.
By default, \texttt{smuggle} statements will install missing packages (and any
missing dependencies of those packages) into a notebook-specific, virtual
environment-like directory called a ``project'' (see
Sec.~\ref{subsec:projects}). In turn, \texttt{smuggle} statements executed in a
particular notebook will preferentially load packages from the notebook's
project directory whenever they are available, rather than searching for them
in the user's main Python environment. In this way, \texttt{smuggle}
statements can be substituted for \texttt{import} statements to automatically
ensure that all packages needed to run a notebook are installed and available
at runtime each time the notebook is run, without risking interfering with
dependencies of the user's other Python programs, or other Davos-enhanced
notebooks.
